---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggppt

<!-- badges: start -->
<!-- badges: end -->

A `ggplot2` extension which has geoms for common shapes and elements in PowerPoint

## Installation

You can install the development version of ggppt from [GitHub](https://github.com/) with:

``` r
devtools::install_github("doehm/ggppt")
```

## geoms

A list of geoms currently included:

* `geom_arrow`
* `geom_callout`
* `geom_chevron`
* `geom_cross`
* `geom_diamond`
* `geom_elbow`
* `geom_parallelogram`
* `geom_pentagon`
* `geom_triangle`

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggppt)
suppressMessages(library(tidyverse))

df <- tibble(
  xmin = c(0:3, 5),
  xmax = c(1:4, 8),
  ymin = 3,
  ymax = 4
)

df |>
  ggplot(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = 1:5)) +
  geom_arrow(head_length = 0.15) +
  scale_fill_gradient2() +
  coord_fixed()

```
